Air cargo load and route planning in pickup and delivery operations

### 2023-06-08 CAIE/results.tex
cie file updated and experimentations almost ended

\begin{table}[H]
\centering
\caption{Solutions with volume {\color{red}$surplus =1.2$} and 3600s as time limit.}  \label{tab:20}
\footnotesize
\begin{tabular}{ccccccccc}
\toprule
{\bf Tours}&$method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
\toprule
\multirow{4}{*}{ \specialcell{$\pi_{TSP_1}$\\ $\pi_{TSP_2}$ }} &\multirow{2}{*}{\it Gurobi* } & $f$ & 8.52    & 11.70   & 13.07   & 13.54 & 12.44     &  1.00\\ % 5927
&&               {\bf run time (s)}  & 17      & 17       & 16      & 17   & 26        &  1.0 \\ % 93
\cmidrule(lr){2-9}	
&\multirow{2}{*}{\it Shims}    & $f$ & 7.83    & 11.34   & 12.77   & 13.20 & 12.22     &  0.97 \\ % 5736
&&         {\bf run time (s)}        & 4       & 5       &  6      & 7     & 10        &  2.9  \\ % 32

@@

\multirow{4}{*}{\it $S_{K}$ }&\multirow{2}{*}{\it Gurobi* } & $f$ & 8.51    & 12.25   & 13.32   & 14.61  & x        & 1.00 \\ % 4869
&&               {\bf run time (s)}  & 25      & 36      & 121     & 297    & x        &  1.0 \\ % 479
\cmidrule(lr){2-9}	
&\multirow{2}{*}{\it Shims}    & $f$ & 8.11    & 12.18   & 13.25   & 14.57  & 14.33    &  0.99 \\ % 4811
&&         {\bf run time (s)}        & 4       & 8       & 33      & 95     & 572      &  3.4  \\ % 140
\bottomrule
\multicolumn{9}{c}{*{\it MIPgap} parameter set to 1\%. The $f$ values are \textpm 1\% distant from the optimal solution}\\

@@

\begin{table}[H]
	\centering
	\caption{Solutions with volume {\color{blue}$surplus=1.5$} and 3600s as time limit.}  \label{tab:50}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\bf Tours} & $method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ \specialcell{$\pi_{TSP_1}$\\ $\pi_{TSP_2}$ }} & \multirow{2}{*}{\it Gurobi* } & $f$ & 11.80 & 16.74 & 18.04 & 18.86 & 16.92 & 1.00 \\ % 8236
		&&               {\bf run time (s)}  & 38    & 30    & 27    & 29    & 81    & 1.00  \\ % 205
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{\it Shims}    & $f$ & 10.89 & 16.65 & 17.80 & 18.69 & 16.45 & 0.98  \\ % 8048
		&&         {\bf run time (s)}        & 4     & 5     & 6     & 7     & 8     & 7.1   \\ % 29

@@

		\multirow{4}{*}{\it $S_{K}$ } & \multirow{2}{*}{\it Gurobi* } & $f$ & 11.81 & 17.01 & 18.25 & 20.59 & 18.36   & 1.00 \\ % 8602
		&&               {\bf run time (s)}  & 53    & 61    & 193   & 470   & 2241    & 1.0  \\ % 3018
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{\it Shims}    & $f$ & 11.33 & 16.97 & 17.56 & 20.43 & 17.94   & 0.98  \\ % 8423
		&&         {\bf run time (s)}        & 4     & 8     & 34    & 96    & 591     & 4.1 \\ % 733
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with volume {\color{violet}$surplus=2.0$} and 3600s as time limit.}  \label{tab:100}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\bf Tours} & $method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ \specialcell{$\pi_{TSP_1}$\\ $\pi_{TSP_2}$ }} & \multirow{2}{*}{\it Gurobi* } & $f$ & 17.75 & 24.39 & 26.46 & 27.09 & 24.00 & 1.00 \\ % 119.69
		&&                                                                               {\bf run time (s)}  & 162   & 95    & 74    & 68    & 67    & 1.0  \\ % 466
		\cmidrule(lr){2-9}	
		&                                                                   \multirow{2}{*}{\it Shims} & $f$ & 16.73 & 24.06 & 26.15 & 26.25 & 23.54 &  0.97 \\ % 116,48
		&&                                                                                {\bf run time (s)} & 5     & 6     & 8     & 10    & 11    &  11.7  \\ % 40

@@

		                                 \multirow{4}{*}{\it $S_{K}$ } & \multirow{2}{*}{\it Gurobi* } & $f$ & 17.75 & 25.24 & 26.46 & 29.11 &  x   & 1.00 \\ % 9856
		&&                                                                                {\bf run time (s)} & 151   & 123   & 319   & 689   &  x   & 1.0  \\ % 1282
		\cmidrule(lr){2-9}	
		&                                                                \multirow{2}{*}{\it Shims}    & $f$ & 16.88 & 24.30 & 26.24 & 28.65 & 28.74 & 0.97  \\ % 9607
		&&                                                                                {\bf run time (s)} & 5     & 9     & 37    & 108   & 625   & 8.1  \\ % 159
		\bottomrule

@@

{\color{blue}
{\it Gurobi*} could not solve scenario 5 in Table \ref{tab:100} because $3600/K! = 0.71s$, not enough time for {\it Gurobi*} to find a feasible node solution.
}

@@

		\multirow{6}{*}{\it Gurobi* }& \multirow{2}{*}{1200} & $f$ & 14.67   & x       &  20.64  &  x      & 27.97   & x \\ % 
		&        &  {\bf run time (s)}                             & 217     & x       &  304    &  x      & 579     & x \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.59   & 13.59   &  20.60  &  x      & 29.10   & x \\ % 
		&        &  {\bf run time (s)}                             & 313     & 1460    &  327    &  x      & 543     & x \\ % 
		\cmidrule(lr){2-9}                              		
		& \multirow{2}{*}{3600}& $f$                               & 14.61   & x       &  20.59  & 18.36   & 29.11   & x \\ % 
		&        &  {\bf run time (s)}                             & 297     & x       &  470    & 2241    & 689     & x \\ % 		
		\midrule
		\multirow{6}{*}{\it Shims}   & \multirow{2}{*}{1200} & $f$ & 15.14   &         &         &         &         &   \\ % 
		&        & {\bf run time (s)}                              & 73      &         &         &         &         &   \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               &         &         &         &         &         &   \\ % 
		&        &  {\bf run time (s)}                             &         &         &         &         &         &   \\ % 	
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{3600} & $f$                              & 14.57   & 14.33   &  20.43  & 17.94   & 28.65   & 28.74 \\ %  
		&        &  {\bf run time (s)}                             &  95     &  572    &  96     & 591     & 108     &  625  \\ %  	                                        
		\bottomrule

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
	\begin{axis}[
		area style,
		]
		\addplot+[ybar interval,mark=no] plot coordinates { 
			(0,.3)
			(1,.5)
			(2,.6)
			(3,.5)
			(4,.25)
			(5,.1)
			(6,.5)
			(7,.25)
			(8,.1)
		};
	\end{axis}
\end{tikzpicture}
\captionof{figure}{ESTE GRÁFICO É APENAS UM MODELO}
\end{figure}

@@

\multirow{2}{*}{$1.2$}   & Least cost    & 7.83    & 11.34 & 12.77 & 13.20 & 12.22  & 57.36 &       \\ 
                         & Best in $K!$  & 8.11    & 12.18 & 13.25 & 14.57 & 14.33  & 62.44 & 8.9\%  \\ 
\midrule[.1pt]	
\multirow{2}{*}{$1.5$}   & Least cost    & 10.89   & 16.65 & {\color{red}17.80} & 18.69 & 16.45  & 80.48 & \\ 	
                         & Best in $K!$  & 11.33   & 16.97 & 17.56 & 20.43 & 17.94  & 84.23 & 4.8\%  \\ 
\midrule[.1pt]	
\multirow{2}{*}{$2.0$}   & Least cost    & 16.73   & 24.06 & 26.15 & 26.25 & 23.54  & 116.73&  \\ 
                         & Best in $K!$  & 16.88   & 24.30 & 26.24 & 28.65 & 28.74  & 124.81& 6.7\%   \\ 		                         
\midrule[.1pt]
\multicolumn{8}{r}{{\bf K! strategy advantage}}                                              & {\bf 6.8}\% \\

>>>>

\begin{table}[H]
\centering
\caption{Solutions with volume {\color{red}$surplus =1.2$} and 3600s as time limit.}  \label{tab:20}
\footnotesize
\begin{tabular}{ccccccccc}
\toprule
{\bf Tours}&$method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
\toprule
\multirow{4}{*}{ \specialcell{$\pi_{TSP_1}$\\ $\pi_{TSP_2}$ }} &\multirow{2}{*}{\it Gurobi* } & $f$ & 8.52    & 11.70   & 13.07   & 13.54 & 12.44     &  1.00\\ % 5927
&                                                               &               {\bf run time (s)}  & 17      & 17      & 16      & 17    & 26        &  1.0 \\ % 93
\cmidrule(lr){2-9}	
&                                                               \multirow{2}{*}{\it Shims}    & $f$ & 8.54    & 11.63   & 12.97   & 13.43 & 12.36     &  0.99 \\ % 5893
&                                                               &         {\bf run time (s)}        & 1       & 1       & 2       & 2     & 2         &  11.6 \\ % 8

@@

\multirow{4}{*}{\it $S_{K}$ }&                                  \multirow{2}{*}{\it Gurobi* } & $f$ & 8.52    & 12.25   & 13.32   & 14.61  & x        & 1.00 \\ % 4869
&                                                               &               {\bf run time (s)}  & 25      & 36      & 121     & 297    & x        &  1.0 \\ % 479
\cmidrule(lr){2-9}	
&                                                               \multirow{2}{*}{\it Shims}    & $f$ & 8.54    & 12.26   & 13.23   & 14.53  & 13.42    & 0.99  \\ % 4813
&                                                               &         {\bf run time (s)}        & 1       & 2       & 6       & 17     & 106      & 18.4   \\ % 132
\bottomrule
\multicolumn{9}{c}{*{\it MIPgap} parameter set to 1\%. The $f$ values are \textpm 1\% distant from the optimal solution}\\

@@

\begin{table}[H]
	\centering
	\caption{Solutions with volume {\color{blue}$surplus=1.5$} and 3600s as time limit.}  \label{tab:50}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\bf Tours} & $method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ \specialcell{$\pi_{TSP_1}$\\ $\pi_{TSP_2}$ }} & \multirow{2}{*}{\it Gurobi* } & $f$ & 11.80 & 16.74 & 18.04 & 18.86 & 16.92 & 1.00 \\ % 8236
		&&               {\bf run time (s)}                                                                  & 38    & 30    & 27    & 29    & 81    & 1.00  \\ % 205
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{\it Shims}                                                                    & $f$ & 11.83 & 16.74 & 18.01 & 18.89 & 16.91 & 1.00  \\ % 
		&&         {\bf run time (s)}                                                                        & 1     & 2     & 2     & 3     & 3     & 20.5  \\ %

@@

		\multirow{4}{*}{\it $S_{K}$ } & \multirow{2}{*}{\it Gurobi* }                                  & $f$ & 11.81 & 17.01 & 18.25 & 20.59 & 18.36   & 1.00 \\ % 8602
		&&               {\bf run time (s)}                                                                  & 53    & 61    & 193   & 470   & 2241    & 1.0  \\ % 3018
		\cmidrule(lr){2-9}	
		&\multirow{2}{*}{\it Shims}                                                                    & $f$ & 11.83 & 17.00 & 18.21 & 20.45 & 18.00   & 0.99  \\ % 8549
		&&         {\bf run time (s)}                                                                        & 1     & 2     & 9     & 26    & 157     & 15.5 \\ % 195
		\bottomrule

@@

\begin{table}[H]
	\centering
	\caption{Solutions with volume {\color{violet}$surplus=2.0$} and 3600s as time limit.}  \label{tab:100}
	\footnotesize
	\begin{tabular}{ccccccccc}
		\toprule
		{\bf Tours} & $method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{4}{*}{ \specialcell{$\pi_{TSP_1}$\\ $\pi_{TSP_2}$ }} & \multirow{2}{*}{\it Gurobi* } & $f$ & 17.75 & 24.39 & 26.46 & 27.09 & 24.00 & 1.00 \\ % 11969
		&&                                                                               {\bf run time (s)}  & 162   & 95    & 74    & 68    & 67    & 1.0  \\ % 466
		\cmidrule(lr){2-9}	
		&                                                                   \multirow{2}{*}{\it Shims} & $f$ & 17.78 & 24.40 & 26.36 & 27.01 & 23.94 & 0.99  \\ % 11949
		&&                                                                                {\bf run time (s)} & 2     & 3     & 3     & 4     & 5     & 27.4  \\ % 17

@@

		                                 \multirow{4}{*}{\it $S_{K}$ } & \multirow{2}{*}{\it Gurobi* } & $f$ & 17.75 & 25.24 & 26.46 & 29.11 &  x   & 1.00 \\ % 9856
		&&                                                                                {\bf run time (s)} & 151   & 123   & 319   & 689   &  x   & 1.0  \\ % 1282
		\cmidrule(lr){2-9}	
		&                                                                \multirow{2}{*}{\it Shims}    & $f$ & 17.78 & 25.25 & 26.38 & 28.98 & 26.08 & 1.00  \\ % 9839
		&&                                                                                {\bf run time (s)} & 2     & 3     & 13    & 37    & 229   & 23.3  \\ % 284
		\bottomrule

@@

{\color{blue}
{\it Gurobi*} could not solve scenario 5 in Table \ref{tab:100} because $3600/K! = 0.71s$ is not enough time for {\it Gurobi*} to find a feasible node solution.
}

@@

		\multirow{6}{*}{\it Gurobi* }& \multirow{2}{*}{1200} & $f$ & 14.67   & x       &  20.64  &  x      & 27.97   & x \\ % 
		&        &  {\bf run time (s)}                             & 217     & x       &  304    &  x      & 579     & x \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.59   &         &  20.60  &  x      & 29.10   & x \\ % 
		&        &  {\bf run time (s)}                             & 313     &         &  327    &  x      & 543     & x \\ % 
		\cmidrule(lr){2-9}                              		
		& \multirow{2}{*}{3600}& $f$                               & 14.61   & x       &  20.59  &         & 29.11   & x \\ % 
		&        &  {\bf run time (s)}                             & 297     & x       &  470    &         & 689     & x \\ % 		
		\midrule
		\multirow{6}{*}{\it Shims}   & \multirow{2}{*}{1200} & $f$ & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        & {\bf run time (s)}                              & 18      & 109     &  26     & 160     & 37      & 203   \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        &  {\bf run time (s)}                             & 18      & 107     &  25     & 159     & 37      & 192   \\ % 	
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{3600} & $f$                              & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ %  
		&        &  {\bf run time (s)}                             & 17      & 106     &  26     & 157     & 37      & 181   \\ %  
		\bottomrule

		&                                       & {\bf Normalized} & 0.99    & x       & 0.99    & x       & 1.00    & x\\
		&                                       & {\bf Speed-up}   & 15.6    & x       & 14.3    & x       & 16.3    & x\\

		\bottomrule

@@

@@

\multirow{2}{*}{$1.2$}   & Least cost    & 8.54    & 11.63   & 12.97   & 13.43  & 12.36 & 58.93 &       \\ 
                         & Best in $K!$  & 8.54    & 12.26   & 13.23   & 14.53  & 13.42 & 61.98 & 5.2\%  \\ 
\midrule[.1pt]	
\multirow{2}{*}{$1.5$}   & Least cost    & 10.89   & 11.83   & 16.74   & 18.01  & 18.89 & 76.36 & \\ 	
                         & Best in $K!$  & 11.33   & 11.83   & 17.00   & 18.21  & 20.45 & 78.82 &  3.2\%  \\ 
\midrule[.1pt]	
\multirow{2}{*}{$2.0$}   & Least cost    & 17.78   & 24.40   & 26.36   & 27.01  & 23.94 & 119.49 &  \\ 
                         & Best in $K!$  & 17.78   & 25.25   & 26.38   & 28.98  & 26.08 & 124.47 & 4.2\%   \\ 		                         
\midrule[.1pt]
\multicolumn{8}{r}{{\bf K! strategy advantage}}                                              & {\bf 4.2}\% \\
